% --- APPENDIX ---
\section{Assumptions}
\label{app:derivation}
% Full Maxwell → Reciprocity → V_n derivation
% Born approximation formal conditions
% RLC parameter extraction
% S-parameter network theory

The electromag netic environment is modeled as a time-harmonic system at the PT frequency ($f_{PT}=62.5MHz$ at $1.5T$ and $f_{PT}=122.5MHz$ at 3T) with $\omega=2\pi f_{PT}$.

Maxwells curl equations in the source region are:

\begin{align}
    \nabla \times \mathbf{E} = -j\omega\mu_0 \mathbf{H} \label{maxwell1}\\
    \nabla \times \mathbf{H} = \mathbf{J}_{src} + (\sigma+j\omega\epsilon)\mathbf{E} \label{maxwell2}
\end{align}

where $\mathbf{J}_{src}$ is the current density in the transmit loop (zero elsewhere), $\sigma$ is the electrical conductivity, $\epsilon$ is the permittivity and $\mu_0$ is the permeability of free space.

To simplify the derivation, we make the following assumptions:
\begin{itemize}
    \item all media are linear and \rev{isotropic}
    \item all media are non-magnetic, i.e. relative permeability is $\mu_r=1$ everywhere so that $\mathbf{B}=\mu_0 \mathbf{H}$
    \item the system is in a steady-state at frequency $\omega$. Transient motion effects are ignored as the time scale is orders of magnitude lower.
    \item Tissue properties are real-valued everywhere. We use complex admittivity defined as $\gamma = \sigma + j\omega\epsilon$
\end{itemize}

\section{Lorentz Reciprocity Theorem}

Consider two distinct electromagnetic configurations (a) and (b) applied to the same electromagnetic environment (same $\sigma(\rev{\mathbf{r}}), \epsilon(\rev{\mathbf{r}})$ and $\mu_0$), each with its own source and fields:

Configuration (a): source $\mathbf{J}^a$ on the loop conductor, zero elsewhere and fields $\mathbf{E}^a$ and $\mathbf{H}^a$

Configuration (b): source $\mathbf{J}^b$ and fields $\mathbf{E}^b$ and $\mathbf{H}^b$

We now seek to describe the Lorentz reciprocity identity which describes the coupling of fields produced by one source and received by the other and vice versa

\begin{align}
    \label{lorentzreciprocity}
    \rev{\nabla \cdot} (\mathbf{E}^a \times \mathbf{H}^b - \mathbf{E}^b \times \mathbf{H}^a) = \rev{\nabla \cdot}(\mathbf{E}^a \times \mathbf{H}^b) - \rev{\nabla \cdot}(\mathbf{E}^b \times \mathbf{H}^a)
\end{align}

in terms of only sources and material parameters:

Using the product rule on the first term of \eqref{lorentzreciprocity}

\begin{align}
    \rev{\nabla \cdot}(\mathbf{E}^a \times \mathbf{H}^b) = \mathbf{H}^b \rev{\cdot} (\nabla \times \mathbf{E}^a) - \mathbf{E}^a \rev{\cdot} (\nabla \times \mathbf{H}^b)
\end{align}

Substituting Eq.\eqref{maxwell1} and Eq.\eqref{maxwell2} and using complex admittivity we arrive at 

\begin{align}
    \rev{\nabla \cdot}(\mathbf{E}^a \times \mathbf{H}^b) = \mathbf{H}^b \rev{\cdot} (-j \omega \mu_0 \mathbf{H}^a) - \mathbf{E}^a \rev{\cdot} (\mathbf{J}^b + \gamma \mathbf{E}^b) \\
    = -j \omega \mu_0 (\mathbf{H}^b \rev{\cdot} \mathbf{H}^a) - \mathbf{E}^a \rev{\cdot} \mathbf{J}^b - \gamma(\mathbf{E}^a \rev{\cdot} \mathbf{E}^b)
\end{align}

\rev{Similarly} for the second term of Eq.\eqref{lorentzreciprocity} we get

\begin{align}
    \rev{\nabla \cdot}(\mathbf{E}^b \times \mathbf{H}^a) = -j \omega \mu_0 (\mathbf{H}^a \rev{\cdot} \mathbf{H}^b) - \mathbf{E}^b \rev{\cdot} \mathbf{J}^a - \gamma(\mathbf{E}^b \rev{\cdot} \mathbf{E}^a)
\end{align}

Equation \eqref{lorentzreciprocity} is the difference of these two divergences:

Collecting term by term 
\begin{align}
    -j\omega\mu_0 (\mathbf{H}^a \rev{\cdot} \mathbf{H}^b) - (-j \omega \mu_0 (\mathbf{H}^a \rev{\cdot} \mathbf{H}^b)) = 0 \\
    -\gamma (\mathbf{E}^a \rev{\cdot} \mathbf{E}^b) - (-\gamma (\mathbf{E}^b \rev{\cdot} \mathbf{E}^a)) = -\gamma (\mathbf{E}^a \rev{\cdot} \mathbf{E}^b) +\gamma (\mathbf{E}^a \rev{\cdot} \mathbf{E}^b) = 0 \\
    -\mathbf{E}^a \rev{\cdot} \mathbf{J}^{\rev{b}} -(-\mathbf{E}^b \rev{\cdot} \mathbf{J}^a) = \mathbf{E}^b \rev{\cdot} \mathbf{J}^a - \mathbf{E}^a \rev{\cdot} \mathbf{J}^b
\end{align}

only $\mathbf{E}^b \rev{\cdot} \mathbf{J}^a - \mathbf{E}^a \rev{\cdot} \mathbf{J}^b$ remains and 

\begin{align}
\label{before_reciprocity}
    \rev{\nabla \cdot} (\mathbf{E}^a \times \mathbf{H}^b - \mathbf{E}^b \times \mathbf{H}^a) = \mathbf{E}^b \rev{\cdot} \mathbf{J}^a - \mathbf{E}^a \rev{\cdot} \mathbf{J}^b
\end{align}

Note that these cancellations require the above assumptions/simplifications that all tissue characteristics are \rev{isotropic} (scalar $\sigma$, $\epsilon$ $\rightarrow$ symmetric $\gamma$) and nonmagnetic (uniform $\mu_0$).

Integrating Eq. \eqref{before_reciprocity} over a volume $V$ bounded by a closed surface $S$ we find 

\begin{align}
    \label{reciprocity}
    \oiiint_{S} (\mathbf{E}^a \times \mathbf{H}^b - \mathbf{E}^b \times \mathbf{H}^a) \rev{\cdot} dS = \iiint_{V} (\mathbf{E}^b \rev{\cdot} \mathbf{J}^a - \mathbf{E}^a \rev{\cdot} \mathbf{J}^b) dV
\end{align}

the general Lorentz reciprocity theorem for lossy, dispersive, isotropic media \cite{Harrington2001Time-harmonicFields}

At an arbitrary port $n$, the fields on the cross section can be expressed in terms of the ports voltage $V_p$ and current $I_p$ via the transmission line mode (citation pending):

\begin{align}
    \label{harringtonTLM}
    \int_{port \quad p}(\mathbf{E}^a \times \mathbf{H}^b - \mathbf{E}^b \times \mathbf{H}^a)dS = V_p^a I_p^b - V_p^b I_p^a
\end{align}

Summing over all N+1 ports:

\begin{align}
    \sum_{p=0}^{N} [V_p^a I_p^b -V_p^b I_p^a] = 0
\end{align}

For a two-port subset, where port 1 is driven in configuration a, port n is driven in configuration b and all other ports terminated we get:

\begin{align}
    V_1^a I_1^b + V_n^a I_n^b = V_1^b I_1^a + V_n^b I_n^a
\end{align}

In configuration a, port n is terminated (load $Z_0$ only, \rev{no} source) so the voltage at port n is purely due to coupling $ \rightarrow V_n^a = $ \rev{received} voltage from PT. In configuration b, port 1 is terminated, so $V_1^b =$ \rev{received} voltage from driven coil n.

For matched terminations and equal drive levels this yields the standard result:

\begin{align}
    \label{PortReciprocity}
    \frac{V_n^a}{I_1^a} = \frac{V_1^b}{I_n^b} \equiv Z_{n,1}
\end{align}

wherein $Z_{n,1}$ is the \rev{transimpedance} between port 1 and port n.



\begin{figure}[htbp]
\centering
\begin{tikzpicture}[
    scale=0.75, transform shape,
    coil/.style={draw, thick, minimum width=0.8cm, minimum height=1.2cm, rounded corners=2pt},
    body/.style={draw, thick, fill=gray!15, rounded corners=8pt},
    port/.style={draw, fill=white, circle, inner sep=1pt, font=\scriptsize},
    arr/.style={->, thick, >=stealth},
    lbl/.style={font=\small}
]

% --- Configuration (a): PT loop drives ---
\node[font=\normalsize\bfseries] at (3.5, 5.2) {Configuration (a)};

% Body
\node[body, minimum width=4cm, minimum height=3cm] (bodyA) at (3.5, 2) {};
\node[font=\scriptsize, gray] at (3.5, 2) {$\gamma(\mathbf{r}) = \sigma + j\omega\varepsilon$};

% PT loop (port 1) - left
\node[coil, fill=blue!15] (ptA) at (0.3, 2) {};
\node[font=\scriptsize, above] at (ptA.north) {PT loop};
\node[port] at (ptA.south) {1};
\draw[arr, blue!70!black] (-0.8, 2.5) -- (ptA.west) node[midway, above, font=\scriptsize] {$I_1$};
\node[font=\scriptsize, blue!70!black, below] at (0.3, 0.1) {\textbf{Driven}};

% RX coil (port n) - right
\node[coil, fill=red!10] (rxA) at (6.7, 2) {};
\node[font=\scriptsize, above] at (rxA.north) {Coil $n$};
\node[port] at (rxA.south) {$n$};
\draw[arr, red!70!black] (rxA.east) -- (8.0, 2) node[midway, above, font=\scriptsize] {$V_n^a$};
\node[font=\scriptsize, red!70!black, below] at (6.7, 0.1) {Terminated ($Z_0$)};

% H-field arrows through body
\draw[->, thick, blue!50, dashed] (1.5, 3.0) to[bend left=15] (5.5, 3.0);
\node[font=\scriptsize, blue!50] at (3.5, 3.8) {$\mathbf{H}_1, \mathbf{E}_1$};

% --- Configuration (b): Coil n drives ---
\node[font=\normalsize\bfseries] at (13, 5.2) {Configuration (b)};

% Body
\node[body, minimum width=4cm, minimum height=3cm] (bodyB) at (13, 2) {};
\node[font=\scriptsize, gray] at (13, 2) {$\gamma(\mathbf{r}) = \sigma + j\omega\varepsilon$};

% PT loop (port 1) - left
\node[coil, fill=blue!10] (ptB) at (9.8, 2) {};
\node[font=\scriptsize, above] at (ptB.north) {PT loop};
\node[port] at (ptB.south) {1};
\draw[arr, blue!70!black] (ptB.west) -- (8.5, 2) node[midway, above, font=\scriptsize] {$V_1^b$};
\node[font=\scriptsize, blue!70!black, below] at (9.8, 0.1) {Terminated ($Z_0$)};

% RX coil (port n) - right
\node[coil, fill=red!15] (rxB) at (16.2, 2) {};
\node[font=\scriptsize, above] at (rxB.north) {Coil $n$};
\node[port] at (rxB.south) {$n$};
\draw[arr, red!70!black] (17.5, 2.5) -- (rxB.east) node[midway, above, font=\scriptsize] {$I_n$};
\node[font=\scriptsize, red!70!black, below] at (16.2, 0.1) {\textbf{Driven}};

% H-field arrows through body (reversed)
\draw[->, thick, red!50, dashed] (15.0, 3.0) to[bend left=15] (11.0, 3.0);
\node[font=\scriptsize, red!50] at (13, 3.8) {$\mathbf{H}_n, \mathbf{E}_n$};

% Reciprocity result
\node[draw, rounded corners, fill=yellow!10, inner sep=6pt, font=\small] at (8.25, -1.2) {
    Reciprocity: $\displaystyle Z_{n,1} = \frac{V_n^a}{I_1^a} = \frac{V_1^b}{I_n^b} = Z_{1,n}$
};

\end{tikzpicture}
\caption{The two configurations used in the Lorentz reciprocity derivation. In configuration (a), the PT source (port 1) is driven and the voltage $V_n^a$ is measured at port $n$. In configuration (b), receive coil $n$ is driven and the voltage $V_1^b$ is measured at port 1. The same tissue environment $\gamma(\mathbf{r})$ is present in both cases. Reciprocity guarantees that the transimpedance is identical: $Z_{n,1} = Z_{1,n}$.}
\label{fig:reciprocity-configs}
\end{figure}

\subsection{Evaluation of the surface integral}

We apply the reciprocity Theorem (Eq. \eqref{lorentzreciprocity}) to the PT system, where configuration (a) is the PT transmitter as port $1$ and configuration (b) is the \rev{receive} element $n$. For a linear, isotropic system, the multi-port network is reciprocal ($Z_{n,1}=Z_{1,n}$).

We now derive the explicit expression for $V_n^a$, the voltage induced at receive port n by the PT transmitter.

We use Eq. \eqref{lorentzreciprocity} and \rev{separate} the volume integral into three non-overlapping regions: $V = V_{ports} \cup V_{body} \cup V_{free}$ where $V_{ports}$ contains the antenna conductors, $V_{body}$ is the tissue volume and $V_{free}$ is free space.

\rev{In} $V_{free}$\rev{:} $\sigma=0$, $\epsilon = \epsilon_0$ \rev{and there are no sources} $\rightarrow$ no contribution to the right side.

In $V_{ports}$ the source contribution is captured by the port terms of Eq. \eqref{harringtonTLM}. In $V_{body}$ there are no impressed sources ($\mathbf{J}^a=\mathbf{J}^b=0$, but $\gamma \neq 0$ since tissue has nonzero $\sigma, \epsilon$.

Splitting the integration volume allows us to rewrite the reciprocity theorem:

In the body volume there are no impressed sources, so
\begin{align}
    \label{Vbody}
    \oint_{S_{body}}(\mathbf{E}^a \times \mathbf{H}^b - \mathbf{E}^b \times \rev{\mathbf{H}}^a)\rev{\cdot}dS = 0
\end{align}

This states that the reciprocity surface integral vanishes over any surface enclosing only passive media - a well known result \cite{Harrington2001Time-harmonicFields}.

To extract $V_n$ we use a different approach. The voltage at a terminated port can be written as \cite{Rumsey1954ReactionTheory}

\begin{align}
    \label{RumseyVoltage}
    \langle a,b \rangle = \iiint_V (\mathbf{E}^a \rev{\cdot} \mathbf{J}^b) dV
\end{align}

where $\rev{\langle a,b \rangle}$ is the "reaction", i.e. the response produced by the fields of configuration $a$ \rev{on} the sources of configuration $b$.

The induced current density in tissue in configuration $b$ is $\mathbf{J}^b=\gamma \mathbf{E}^b$.
According to \cite{Rumsey1954ReactionTheory} the power observable at port $n$ is simply the product of port voltage and port current $\rev{\langle a,b \rangle}=V_n I_n$. With current normalized to $I_n=1A$, Eq. \eqref{RumseyVoltage} over the Volume $V_{body}$ is therefore

\begin{align}
    \label{PortVoltage}
    V_n = \iiint_{V_{body}} \mathbf{E}^a \rev{\cdot} \mathbf{J}^b dV \\
    V_n = \iiint_{V_{body}} \gamma (\mathbf{E}^a \rev{\cdot} \mathbf{E}^b) dV
\end{align}

This equation states that the received voltage at port $n$ $V_n$ equals the volume integral of the tissue admittivity $\gamma$ weighted by the overlap of the transmitter and receiver electric field - the coils sensitivity profile.

\subsection{Origin of the electric fields in electrically small source}

\rev{Henceforth we identify configuration (a) with the PT source (port 1) and configuration (b) with receive element n, writing $\mathbf{E}_1 \equiv \mathbf{E}^a$ and $\mathbf{E}_n \equiv \mathbf{E}^b$.}

The PT loop antennas size ($d=30mm$ in our simulations) is electrically small compared to the wavelength. The electrical size parameter is defined as $ka$ where $k=2 \pi / \lambda_0$\rev{,} the wave number in free space and $a=\rev{0.015}\,\rev{\mathrm{m}}$ is the loop radius, so $ka\rev{\approx 0.02}$ at $62.5MHz$ and $ka\rev{\approx 0.04}$ at $122.5MHz$. 

In an electrically small antenna ($ka \rev{\ll} 1$) the loop radiates primarily as a magnetic dipole while the produced E-field is \rev{suppressed} by a factor $ka$ \rev{relative} to a plane wave.

It is important to note that, as the radiated E-field is small, the Faraday induced E-field inside the body ($\mathbf{E}_{ind} \propto \omega \mu_0 \rev{a_{\mathrm{tissue}}}$) is dominant and scales with body dimension where $\rev{a_{\mathrm{tissue}}}$ is the characteristic radius of the human torso.

The total electric field in any region is governed by Faraday's law. This Faraday-induced field is:

\begin{align}
    \label{inducedField}
    \nabla \times \mathbf{E}^a = -j \omega \mu_0 \mathbf{H}^a
\end{align}

In free-space near the loop, $|\mathbf{H}^a| \rev{\gg} |\mathbf{E}^a|$, however, inside the conducting body, the time-varying magnetic field induces an electric field. This Faraday-Field is

\begin{align}
    \label{FaradayField}
    \mathbf{E}_1^{ind} \quad \rev{\text{satisfying}} \quad \nabla \times \mathbf{E}_1^{ind} = -j \omega \mu_0 \mathbf{H}_1
\end{align}

with scaling by $\rev{a_{\mathrm{tissue}}}$

\begin{align}
    \label{ScaledFaraday}
    |\mathbf{E}_1^{ind}| \rev{\sim} \omega \mu_0 |\mathbf{H}_1| \rev{a_{\mathrm{tissue}}}
\end{align}

 This induced Faraday field, unlike the loop-generated field, is independent of loop geometry $ka$.

The proportion of generated field vs. induced field can be estimated as follows: Let $|\mathbf{H}_1|=1\rev{\,\mathrm{A/m}}$ at the body surface. Then the loop generated E-fields at 1.5T / 62.5MHz are approximately

\begin{align}
    \label{LoopEField15T}
    |\mathbf{E}_1^{loop}| \approx ka \rev{\,} \eta_0 |\mathbf{H}_1| \approx \rev{0.02} \cdot 377\rev{\,\Omega} \cdot 1\rev{\,\mathrm{A/m}} \approx \rev{7.5\,\mathrm{V/m}} \\
    \label{inducedField15T}
    |\mathbf{E}_1^{ind}| \approx \omega \mu_0 |\mathbf{H}_1| \rev{a_{\mathrm{tissue}}} \approx 3.9 \cdot 10^8 \rev{\,\mathrm{rad/s}} \cdot 1.26 \cdot 10^{-6}\rev{\,\mathrm{H/m}} \cdot  1\rev{\,\mathrm{A/m}} \cdot 0.15\rev{\,\mathrm{m}} \approx 74 \rev{\,\mathrm{V/m}}
\end{align}

and at 3T / 122.5MHz

\begin{align}
    \label{LoopEField3T}
    |\mathbf{E}_1^{loop}| \approx ka \rev{\,} \eta_0 |\mathbf{H}_1| \approx \rev{0.04} \cdot 377\rev{\,\Omega} \cdot 1\rev{\,\mathrm{A/m}} \approx \rev{15\,\mathrm{V/m}} \\
    \label{inducedField3T}
    |\mathbf{E}_1^{ind}| \approx \omega \mu_0 |\mathbf{H}_1| \rev{a_{\mathrm{tissue}}} \approx 7.8 \cdot 10^8 \rev{\,\mathrm{rad/s}} \cdot 1.26 \cdot 10^{-6}\rev{\,\mathrm{H/m}} \cdot  1\rev{\,\mathrm{A/m}} \cdot 0.15\rev{\,\mathrm{m}} \approx 148 \rev{\,\mathrm{V/m}}
\end{align}

with $\rev{a_{\mathrm{tissue}}}=0.15\rev{\,\mathrm{m}}$, $\mu_0=1.26\cdot 10^{-6}\rev{\,\mathrm{H/m}}$ the vacuum permeability and $\eta_0=377\rev{\,\Omega}$ the \rev{free-space} impedance.

\subsection{Decomposition into direct and tissue-mediated coupling}

The received voltage in port n $V_n$ can be decomposed by splitting the domain of integration:

\begin{align}
    \label{VNCouplingFull}
    V_n = \iiint_{\rev{\mathrm{all\,space}}} \gamma (\mathbf{E}_1 \rev{\cdot} \mathbf{E}_n)dV
\end{align}

In free \rev{space} outside the body, $\gamma = j \omega \epsilon_0$, which is purely reactive and represents direct magnetic coupling (or in other words displacement-current coupling).
Inside the body, $\gamma = \sigma + j\omega \epsilon$ includes the conductive (lossy) contribution.

The total coupling between the source and port n can be expressed through mutual impedance:

\begin{align}
    \label{MutualImped}
    Z_{n,1} = Z_{n,1}^{\rev{\mathrm{direct}}} + Z_{n,\rev{1}}^{\rev{\mathrm{tissue}}}
\end{align}

where $Z_{n,1}^{direct} = j \omega M_0$ is the mutual impedance in the absence of conductive tissue. $M_0$ is the mutual inductance between transmit loop and \rev{receive} loop n, determined solely by coil geometry and separation. It is frequency dependent only through the $j \omega$ factor.

$Z_{n,1}^{tissue}$ is the additional impedance arising from the conductive tissue. It represents the coupling path PT loop $\rightarrow$ H-field $\rightarrow$ Faraday-induced E-field in the body $\rightarrow$ eddy-currents $\rightarrow$ secondary H-field $\rightarrow$ \rev{received} at port n. This term depends on the tissue property distribution and therefore changes when cardiac motion redistributes tissue.

The corresponding voltages (with $I_1=1A$ normalized) are:

\begin{align}
    \label{CoouplingVoltages}
    V_n^{\rev{\mathrm{direct}}} = Z_{n,1}^{\rev{\mathrm{direct}}} \cdot I_1 = j \omega M_0 I_1 \\
    V_n^{\rev{\mathrm{tissue}}} = Z_{n,1}^{\rev{\mathrm{tissue}}} \cdot I_1 = I_1 \iiint_{\rev{\mathrm{tissue}}} \gamma (\mathbf{e}_1 \rev{\cdot} \mathbf{e}_n) dV
\end{align}

where $\mathbf{e}_1 = \mathbf{E}_1 \rev{/} I_1$ and $\mathbf{e}_\rev{n} = \mathbf{E}_n \rev{/} I_n$ are the electric fields normalized to unit drive current.




\begin{figure}[htbp]
\centering
% Figure redesigned (clean Venn-style field-overlap schematic); see changes.md #37
\resizebox{\linewidth}{!}{%
\begin{tikzpicture}[scale=1.0]
% Body
\fill[gray!9] (0,0) ellipse (5.5 and 3.2);
\draw[very thick, gray!55] (0,0) ellipse (5.5 and 3.2);
\node[font=\small, gray!55!black] at (0,2.75) {$V_{\mathrm{body}}:\ \gamma=\sigma+j\omega\varepsilon$};
% Venn field regions
\fill[blue!45, opacity=0.38] (-1.35,-0.1) ellipse (2.7 and 2.05);
\fill[red!45, opacity=0.38] (1.35,-0.1) ellipse (2.7 and 2.05);
\draw[blue!55, thick] (-1.35,-0.1) ellipse (2.7 and 2.05);
\draw[red!60, thick] (1.35,-0.1) ellipse (2.7 and 2.05);
% Region labels
\node[font=\small, blue!65!black] at (-2.75,1.15) {$\mathbf{E}_1$ (PT)};
\node[font=\small, red!65!black] at (2.75,1.15) {$\mathbf{E}_n$ (coil $n$)};
\node[font=\small\bfseries, violet!78!black] at (0,0.15) {$\gamma\,(\mathbf{E}_1\!\cdot\!\mathbf{E}_n)$};
\node[font=\scriptsize\itshape, violet!70!black] at (0,-0.5) {sensitivity};
% --- PT transmit loop (left) ---
\draw[blue!70!black, very thick] (-6.3,-0.1) ++(168:0.7) arc (168:-168:0.7);
\draw[->, blue!70!black, very thick] (-7.65,0.046) -- (-6.985,0.046);
\draw[blue!70!black, very thick] (-7.65,-0.246) -- (-6.985,-0.246);
\node[blue!70!black, font=\small] at (-7.5,0.34) {$I_1$};
\node[blue!70!black, font=\small] at (-6.3,-1.1) {PT};
% field arrows PT -> blue region
\draw[->, blue!45, thick] (-5.62,0.25) to[bend left=8] (-3.6,0.5);
\draw[->, blue!45, thick] (-5.62,-0.45) to[bend right=8] (-3.6,-0.7);
% --- Coil n receive loop (right) ---
\draw[red!70!black, very thick] (6.3,-0.1) ++(12:0.7) arc (12:348:0.7);
\draw[red!70!black, very thick] (6.985,0.046) -- (7.65,0.046);
\draw[red!70!black, very thick] (6.985,-0.246) -- (7.65,-0.246);
\fill[red!70!black] (7.65,0.046) circle (1.1pt);
\fill[red!70!black] (7.65,-0.246) circle (1.1pt);
\node[red!70!black, font=\scriptsize] at (7.83,0.19) {$+$};
\node[red!70!black, font=\scriptsize] at (7.83,-0.39) {$-$};
\draw[<->, red!70!black, thick] (8.05,0.046) -- (8.05,-0.246);
\node[red!70!black, font=\small] at (8.45,-0.1) {$V_n$};
\node[red!70!black, font=\small] at (6.3,-1.1) {Coil $n$};
% field arrows coil n -> red region
\draw[->, red!45, thick] (5.62,0.25) to[bend right=8] (3.6,0.5);
\draw[->, red!45, thick] (5.62,-0.45) to[bend left=8] (3.6,-0.7);
% Equation
\node[draw, rounded corners, fill=white, inner sep=5pt, font=\small] (eq) at (0,-4.4) {$\displaystyle V_n=\iiint_{V_{\mathrm{body}}}\gamma\,(\mathbf{E}_1\cdot\mathbf{E}_n)\,dV$};
\draw[->, thick, violet!65] (0,-2.2) -- (eq.north);
\end{tikzpicture}%
}
\caption{\rev{Conceptual illustration of the volume integral formulation. The PT source (port~1, blue) and receive coil $n$ (red) each produce electric fields in the body; the received voltage $V_n$ is the volume integral of the admittivity-weighted field overlap $\gamma(\mathbf{E}_1 \cdot \mathbf{E}_n)$ (violet region). The integrand is largest where both fields are strong and co-aligned --- the measurement's ``sensitivity profile.'' Outside the body, $\gamma = j\omega\varepsilon_0$ contributes only the direct (reactive) coupling path.}}
\label{fig:field-overlap}
\end{figure}

\subsection{Modulation from cardiac motion and the first-order Born approximation}

During the cardiac cycle, the heart contracts and relaxes, causing tissue to redistribute within the thorax. Between cardiac phase $\varphi_1$ and $\varphi_2$ (i.e. maximum and minimum volume):

\begin{align}
    \label{tissueRedist}
    \sigma \rightarrow \sigma + \Delta \sigma \\
    \epsilon \rightarrow \epsilon + \Delta \epsilon
\end{align}

where $\Delta \sigma$ and $\Delta \epsilon$ are nonzero only in the cardiac displacement Volume $V_{\Delta}$ - the region where tissue identity has changed (e.g. blood replacing myocardium).

The change in voltage is

\begin{align}
    \label{replaceVoltage}
    \Delta V_n = V_{n\varphi_1} - V_{n\varphi_2}
\end{align}

The first-order Born approximation (\cite{Chew1995MathematicalTheory}, Chap 8.10) is a linearization of the field scattering problem in which the total field inside a perturbed region is approximated by the unperturbed (incident) field.
This assumes, that the secondary field produced by the perturbation is negligible compared to the primary field, i.e. $|E_{\rev{\mathrm{scattered}}}| \rev{\ll} |E_{\rev{\mathrm{incident}}}|$ (and $|B_{\rev{\mathrm{scattered}}}| \rev{\ll} |B_{\rev{\mathrm{incident}}}|$). This is the case when the scattering object is electrically small and/or weakly contrasting in its electrical parameters compared to the background.
In the present \rev{context}, the "perturbation" is not the entire body (which produces substantial loading), but rather the redistribution of tissue during cardiac motion (a volume $V_{\Delta} \approx 250mL$, based on typical stroke volume) with admittivity contrast $|\frac{\Delta \gamma}{\gamma}| \approx 0.5$. Since this displacement volume is small compared to the total body volume, the illuminated volume of each \rev{receive} element and even the typical wavelength in tissue, the condition(s) for the Born application are satisfied. Experimental and simulation results for cardiac modulation depths of $M_n<1\%$ further validate the assumption, that the secondary/scattered field is extremely small compared to the primary/incident field.
This allows us to write the signal change $\Delta V_n$ as a linear function of $\Delta\gamma$ weighted by the unperturbed field overlap, without requiring more complex iterative solutions:

\begin{align}
    \label{Born1}
    \Delta V_n \approx \iiint_{V_{\Delta}} [\Delta \sigma + j \omega \Delta \epsilon][\mathbf{E}_1 \rev{\cdot} \mathbf{E}_n] dV
\end{align}

The signal change equals the admittivity change integrated over the displacement volume, weighted by the sensitivity overlap.


\textbf{Note}: we use the term "sensitivity" loosely here as, in the MRI domain, it is more common to think of the sensitivity as the radiated magnetic field rather \rev{than} the electric field. In this particular application, the electric field is generated by eddy-currents induced in conductive tissue - our "sensitivity" therefore is technically the H-field illuminated volume \rev{constrained} by the area therein where $\sigma > 0$


\begin{figure}[htbp]
\centering
% Figure redesigned (clean thorax cross-section, orange V_Delta ring); see changes.md #37
\resizebox{\linewidth}{!}{%
\begin{tikzpicture}[scale=1.0]
% Body (thorax)
\fill[gray!8] (0,0) ellipse (6.3 and 3.6);
\draw[very thick, gray!55] (0,0) ellipse (6.3 and 3.6);
\node[font=\small, gray!55!black] at (-5.0,2.9) {$V_{\mathrm{body}}$};
% Lungs
\fill[cyan!10] (-3.2,0.2) ellipse (1.55 and 2.15);
\draw[cyan!45, thick] (-3.2,0.2) ellipse (1.55 and 2.15);
\node[font=\scriptsize, cyan!45!black] at (-3.2,0.2) {Lung};
\fill[cyan!10] (3.2,0.2) ellipse (1.55 and 2.15);
\draw[cyan!45, thick] (3.2,0.2) ellipse (1.55 and 2.15);
\node[font=\scriptsize, cyan!45!black] at (3.2,0.2) {Lung};
% Heart ED (filled) then ES (covers center -> thin orange ring = small V_Delta)
\fill[orange!35] (0,-0.1) ellipse (1.4 and 1.6);
\fill[red!10] (0,-0.1) ellipse (1.12 and 1.28);
\draw[red!70!black, very thick] (0,-0.1) ellipse (1.4 and 1.6);
\draw[red!55, very thick, dashed] (0,-0.1) ellipse (1.12 and 1.28);
\node[font=\scriptsize, red!45!black] at (0,-0.1) {heart};
% ED / ES labels above body
\node[font=\small, red!70!black] (edl) at (2.6,4.15) {ED ($\varphi_1$)};
\draw[red!70!black, thin] (edl.south) to[bend right=12] (0.82,1.2);
\node[font=\small, red!55!black] (esl) at (-2.6,4.15) {ES ($\varphi_2$)};
\draw[red!55, thin] (esl.south) to[bend left=12] (-0.66,0.98);
% V_Delta label
\node[font=\small\bfseries, orange!78!black] (vd) at (5.4,-2.7) {$V_{\Delta}$};
\draw[->, thick, orange!78!black] (vd.west) to[bend right=10] (1.02,-1.0);
% Anterior / Posterior
\node[font=\scriptsize, gray] at (0,4.15) {Anterior};
\node[font=\scriptsize, gray] at (0,-4.05) {Posterior};
% Compact note box
\node[draw, rounded corners, fill=yellow!8, inner sep=5pt, font=\scriptsize, align=center] at (0,-4.95) {%
$V_{\Delta}\approx 250\,\mathrm{mL}$ (stroke volume) $\ll V_{\mathrm{body}}$,\quad $|\Delta\gamma/\gamma|\approx 0.5$ \ $\Rightarrow$ \ Born approximation valid ($\mathbf{E}_{\mathrm{scat}}\ll\mathbf{E}_{\mathrm{inc}}$)};
\end{tikzpicture}%
}
\caption{\rev{Schematic axial cross-section of the thorax illustrating the cardiac displacement volume $V_{\Delta}$ (orange ring) --- the region where tissue identity changes between end-diastole ($\varphi_1$, solid outline) and end-systole ($\varphi_2$, dashed outline). The first-order Born approximation is valid because $V_{\Delta}$ is small compared to the total body volume and the admittivity contrast is weak ($|\Delta\gamma/\gamma| \approx 0.5$), so the scattered field is negligible compared to the incident field.}}
\label{fig:born-displacement}
\end{figure}

\subsection{Connection to Scattering Parameters}

The scattering parameter $S_{n,1}$ (transmission coefficient from port 1, the PT generator loop, to receive element port n) is defined as the relative incident and reflected waves at each port:

\begin{align}
    \label{ZDef}
    S_{n,1} = \frac{b_n}{a_1}
\end{align}

where $\rev{a}_1 = \frac{V_1^{\rev{\mathrm{inc}}}}{\sqrt{Z_0}}$ is the incident wave amplitude at (transmit) port 1, $b_n = \frac{V_n^{\rev{\mathrm{scattered}}}}{\sqrt{Z_0}}$ is the scattered wave amplitude at (receive) port n, and all other ports are terminated.

The transimpedance $Z_{n,1}$, defined as the open-circuit voltage appearing at port n per unit current driven at port 1

\begin{align}
    \label{transZ}
    Z_{n,1} = \frac{V_n}{\rev{I_1}}
\end{align}

bridges the derivation of the voltage integral (Eq. \eqref{CoouplingVoltages}\rev{)} with the circuital and S-parameter models.

Using the \rev{transimpedance} normalizes out the drive current: the reciprocity integral

\begin{align}
    \label{recInt}
    V_n = I_1 \iiint \gamma (\rev{\mathbf{e}}_1 \cdot \rev{\mathbf{e}}_n) dV
\end{align}

gives $V_n$ for a specific drive current $I_1$. Dividing by $I_1$ yields the \rev{transimpedance} $Z_{n,1}$ - a system property independent of excitation amplitude.

Reciprocity is cleanly contained in the \rev{transimpedance}: Eqn. \eqref{PortReciprocity} directly shows $Z_{n,1} = Z_{1,n}$ - the \rev{transimpedance} is symmetric.

The relationship between $S_{n,1}$ and the \rev{transimpedance} $Z_{n,1}$ is shown below (citation pending):

\begin{align}
    \label{SandZ}
    S_{n,1} = \frac{2Z_0Z_{n,1}}{(Z_0 + Z_{11})(Z_0 + Z_{nn}) - Z_{n,1}^2}
\end{align}

In this application, the inter-port coupling is weak compared to port-port coupling ($|Z_{n,1}| \rev{\ll} |Z_0 + Z_{nn}|$), so

\begin{align}
    \label{SparamWOinterportCoupling}
    S_{n,1} \approx \frac{2Z_0 Z_{n,1}}{(Z_0 + Z_{11})(Z_0 + Z_{nn})}
\end{align}

The port self-\rev{impedances} $Z_{1,1}$ and $Z_{n,n}$ lump together both coil impedance and body loading. Coil \rev{impedance} is unchanged by tissue replacement and coil loading is dominated mainly by local tissue around the coil and not the minute changes in the \rev{comparatively} far away cardiac region.

With $|Z_{n,1}| \rev{\ll} |Z_{\rev{0}} + Z_{1,1}|$ and $|Z_{n,1}| \rev{\ll} |Z_{\rev{0}} + Z_{n,n}|$, the denominator in Eq. \eqref{SparamWOinterportCoupling} is approximately constant between cardiac phases and consequently

\begin{align}
    \label{SParamCouplingSimplified}
    \frac{\Delta S_{n,1}}{S_{n,1}} \approx \frac{\Delta Z_{n,1}}{Z_{n,1}} = \frac{\Delta V_n}{V_n} = M_n
\end{align}

with $M_n$ the modulation depth in receive channel n. The \rev{transimpedance} is the carrier of PT signal modulation.

This also connects this theoretical derivation to the full-wave simulation, where the modulation depth is defined as:

\begin{align}
    \label{TheoryToSim}
    M_n^{sim} = \frac{|S_{n,1}(\varphi_2) - S_{n,1}(\varphi_1)|}{|S_{n,1}(\varphi_1)|}
\end{align}


\subsection{Reduction to Equivalent Circuit Model}

The volume integral formulation (Eq. \eqref{PortVoltage}) can be mapped to a lumped-element equivalent circuit, providing an intuitive formulation of the modulation mechanism:

\textbf{Body loading as an equivalent impedance}

The body-mediated mutual impedance can be written as

\begin{align}
\label{mutImped}
    Z_{n,1}^{body} = \iiint_{body} \gamma (\mathbf{e}_1 \cdot \mathbf{e}_n) dV
\end{align}

\rev{Similarly}, the self-impedance contribution from the body to coil n, the body-loading is

\begin{align}
\label{selfImped}
    Z_{nn}^{body} = \iiint_{body} \gamma |\mathbf{e}_n|^2dV
\end{align}

This complex impedance has real- and imaginary parts

\begin{align}
    Re(Z_{nn}^{body}) = R_{tissue} = \iiint_{body} \sigma|\mathbf{e_n}|^2dV \\
    Im(Z_{nn}^{body}) = X_{tissue} = \omega \iiint_{body} \epsilon |\mathbf{e}_n|^2dV
\end{align}

\textbf{Equivalent RLC circuit}

The \rev{receive} coil element n can be modeled as a series RLC circuit:

\begin{align}
    Z_n = R_{coil} + R_{tissue} + j (\omega L_{coil} - \frac{1}{\omega C_{tune}} + X_{tissue})
\end{align}

where $R_{coil}$ is the coils conductive loss, $L_{coil}$ is the coils self-inductance and $C_{tune}$ is the tuning capacitance.

The loaded and unloaded quality factors are:

\begin{align}
    Q_{unloaded} = \frac{\omega L_{coil}}{R_{coil}} \\
    Q_{loaded} = \frac{\omega L_{coil}}{R_{coil} + R_{tissue}}
\end{align}

At clinical frequencies (0.5T, 1.5T and 3T) body noise dominates, so $R_{\rev{\mathrm{tissue}}} \rev{\gg} R_{\rev{\mathrm{coil}}}$ and $Q_{\rev{\mathrm{loaded}}} \rev{\ll} Q_{\rev{\mathrm{unloaded}}}$ \cite{Edelstein1986TheImaging}.

Figure~\ref{fig:appendix-circuit} shows the equivalent circuit corresponding to this multiport formulation. \rev{It uses the same transformer-coupled representation as the main text (Figure~\ref{fig:equivalent-circuit}) with the tissue admittivity drawn explicitly as $R_e \parallel C_e$; the volume-integral annotations identify the body-mediated mutual impedance $Z_{n,1}^{\mathrm{body}}$, which carries the PT signal, and the per-port self-loading $Z_{nn}^{\mathrm{body}}$, which modifies the coil $Q$-factor.}

\begin{figure}[htbp]
\centering
\resizebox{\linewidth}{!}{%
\begin{circuitikz}[
    every node/.style={font=\small},
    ann/.style={font=\footnotesize\itshape, text=violet}
]
% --- Primary (TX): PT generator loop ---
\draw (0,0) to[sinusoidal voltage source, l=$V_{PT}$] (0,3);
\draw (0,3) to[R, l=$R_{\mathrm{coil},1}$] (3,3);
\draw (3,3) to[cute inductor, l_=$L_1$] (3,0);
\draw (0,0) -- (3,0);
\node[above] at (1.5,3.7) {\textbf{PT generator (primary)}};
% --- Secondary (RX): MR receive coil ---
\draw (6,0) to[cute inductor, l_=$L_n$] (6,3);
\draw (6,3) to[R, l=$R_{\mathrm{coil},n}$] (9,3);
\draw (9,3) to[C, l_=$C_{\mathrm{tune}}$] (9,0);
\draw (6,0) -- (9,0);
\draw (9,3) -- (10,3);
\draw (9,0) -- (10,0);
\node[right] at (10,1.5) {$V_{\mathrm{out}}$};
\draw[<->] (10,0.2) -- (10,2.8);
\node[above] at (7.5,3.7) {\textbf{MR receive coil (secondary)}};
% --- Direct magnetic coupling M_0 ---
\draw[<->, thick, blue!60!black] (3.8,1.5) -- (5.5,1.5);
\node[blue!60!black, font=\footnotesize] at (4.6,1.9) {$M_0$ (direct)};
% --- Body-mediated coupling: tissue admittivity R_e || C_e ---
\draw[violet, thick] (3,0) -- (3,-1.5);
\draw[violet, thick] (6,0) -- (6,-1.5);
\draw (3,-1.5) to[R, l=$R_e$, color=violet] (6,-1.5);
\draw (3,-2.7) to[C, l=$C_e$, color=violet] (6,-2.7);
\draw[violet] (3,-1.5) -- (3,-2.7);
\draw[violet] (6,-1.5) -- (6,-2.7);
% --- Annotations ---
\node[ann] at (4.5,-3.6) {tissue admittivity $\gamma=\sigma+j\omega\varepsilon \equiv R_e \parallel C_e$};
\node[ann] at (4.5,-4.1) {$R_e \propto 1/\sigma$ (eddy),\quad $C_e \propto \varepsilon$ (displacement)};
\node[ann] at (4.5,-4.7) {modulated by cardiac motion $\rightarrow\ M_n = \Delta S_{n,1}/S_{n,1}$};
\node[ann] at (4.5,-5.3) {mutual: $Z_{n,1}^{\mathrm{body}} = \iiint \gamma\,(\mathbf{e}_1 \cdot \mathbf{e}_n)\,dV$};
\node[ann] at (4.5,-5.8) {self-loading: $Z_{nn}^{\mathrm{body}} = \iiint \gamma\,|\mathbf{e}_n|^2\,dV$};
\end{circuitikz}%
}
\caption{\rev{Multiport equivalent circuit derived from the Lorentz reciprocity volume-integral formulation, using the same transformer-coupled representation as the main text (Figure~\ref{fig:equivalent-circuit}). The tissue is drawn explicitly as its complex admittivity $\gamma = \sigma + j\omega\varepsilon \equiv R_e \parallel C_e$, with $R_e \propto 1/\sigma$ and $C_e \propto \varepsilon$. Integrated over the body, the same admittivity produces the body-mediated mutual impedance $Z_{n,1}^{\mathrm{body}} = \iiint \gamma\,(\mathbf{e}_1 \cdot \mathbf{e}_n)\,dV$, which carries the PT signal, and the per-port self-loading $Z_{nn}^{\mathrm{body}} = \iiint \gamma\,|\mathbf{e}_n|^2\,dV$, which modifies the coil $Q$-factor. Cardiac motion modulates $Z_{n,1}^{\mathrm{body}}$ while the self-impedances remain approximately constant, giving $\Delta S_{n,1}/S_{n,1} \approx \Delta Z_{n,1}^{\mathrm{body}}/Z_{n,1}$ (Eq.~\eqref{SParamCouplingSimplified}).}}
\label{fig:appendix-circuit}
\end{figure}


\textbf{Modulation in the RLC model}

Cardiac motion changes the tissue distribution in the illuminated area, causing

\begin{align}
    R_{tissue} \rightarrow R_{tissue} + \Delta R_{tissue} \\
    X_{tissue} \rightarrow X_{tissue} + \Delta X_{tissue}
\end{align}

where

\begin{align}
    \rev{\Delta} R_{\rev{\mathrm{tissue}}} = \iiint_{V_{\Delta}} \Delta \sigma |\mathbf{e}_n|^2 dV \\
    \rev{\Delta} X_{\rev{\mathrm{tissue}}} = \omega \iiint_{V_{\Delta}} \Delta \epsilon |\mathbf{e}_n|^2 dV
\end{align}

These changes in both mutual impedance (Eq. \eqref{mutImped}) and self-impedance (Eq. \eqref{selfImped}) change the transfer function between port 1 and n, so modulation depth is

\begin{align}
    M_n \approx \frac{|\Delta Z_{n,1}^{body}|}{|Z_{n,1}^{direct} + Z_{n,1}^{body}|}
\end{align}

This relation can be further simplified by assuming approximately uniform sensitivity $\mathbf{e}_n$, which is only valid for coils physically larger than the heart and placed in such a way that the heart is well within the sensitivity.

\begin{align}
    M_n \approx \frac{\Delta \sigma_{\rev{\mathrm{eff}}} \times V_{\rev{\Delta}} \times |\mathbf{e}_1 \rev{\cdot} \mathbf{e}_n|^2}{\omega M_0}
\end{align}

where $\Delta \sigma_{\rev{\mathrm{eff}}}$ is the effective conductivity contrast between displaced tissues.


\section{Experimental S-parameter data}\label{app:exp-data}

\revbrown{Tables~\ref{tab:exp-v1}--\ref{tab:exp-v3} list the measured scattering parameter $S_{1,n}$\,(dB) and cardiac modulation depths (magnitude in percent, phase in milliradians) for each individual receive channel and volunteer. The PT generator was driven at 0\,dBm / 62.5\,MHz; S-parameters were derived from the calibrated receiver characteristic. Magnitude modulation depth is the peak-to-peak excursion of the averaged cardiac waveform as a percentage of the mean $S_{1,n}$ level; phase modulation depth is the peak-to-peak phase excursion ($\angle S_{1,n}$ maximum minus minimum) in milliradians.}

\begin{table}[htbp]
\centering
\revbrown{\caption{Volunteer~1: Per-channel S-parameter and cardiac modulation depth. Body~18 (anterior, 18\,ch) + Spine~24 (posterior, 9\,ch). Breathhold 13.7\,s, 20 cardiac cycles averaged.}
\label{tab:exp-v1}
\small
\begin{tabular}{lccc}
\hline
Channel & $S_{1,n}$ (dB) & Mag.\ mod.\ (\%) & Phase mod.\ (mrad) \\
\hline
\multicolumn{4}{l}{\textit{Anterior (Body~18)}} \\
\hline
B22 & $-107.8$ & 0.363 & 70.2 \\
B21 & $-109.2$ & 0.097 & 30.8 \\
B35 & $-113.1$ & 0.091 & 32.8 \\
B36 & $-117.6$ & 0.032 & 25.0 \\
B14 & $-112.0$ & 0.015 & 112.4 \\
B13 & $-103.6$ & 0.008 & 33.4 \\
B31 & $-113.5$ & 0.023 & 53.0 \\
B32 & $-112.6$ & 0.014 & 20.7 \\
B24 & $-107.9$ & 0.069 & 36.1 \\
B23 & $-112.7$ & 0.181 & 122.7 \\
B33 & $-92.8$ & 0.004 & 14.8 \\
B34 & $-113.1$ & 0.040 & 43.4 \\
B12 & $-106.8$ & 0.002 & 48.1 \\
B11 & $-116.7$ & 0.038 & 78.3 \\
B26 & $-116.6$ & 0.042 & 45.7 \\
B25 & $-116.1$ & 0.069 & 31.0 \\
B16 & $-115.3$ & 0.033 & 24.3 \\
B15 & $-116.3$ & 0.048 & 32.7 \\
\hline
\multicolumn{4}{l}{\textit{Posterior (Spine~24)}} \\
\hline
S2T & $-119.3$ & 0.212 & 110.9 \\
S2S & $-118.4$ & 0.125 & 76.3 \\
S2P & $-118.5$ & 0.069 & 73.1 \\
S3P & $-118.3$ & 0.041 & 66.7 \\
S3S & $-118.6$ & 0.063 & 115.8 \\
S3T & $-118.6$ & 0.138 & 87.5 \\
S4T & $-119.5$ & 0.198 & 141.9 \\
S4S & $-119.2$ & 0.042 & 75.7 \\
S4P & $-119.0$ & 0.045 & 97.5 \\
\hline
\end{tabular}}
\end{table}

\begin{table}[htbp]
\centering
\revbrown{\caption{Volunteer~2: Per-channel S-parameter and cardiac modulation depth. Body~12 (anterior, 12\,ch) + Spine~24 (posterior, 12\,ch). Breathhold 17.8\,s, 17 cardiac cycles averaged.}
\label{tab:exp-v2}
\small
\begin{tabular}{lccc}
\hline
Channel & $S_{1,n}$ (dB) & Mag.\ mod.\ (\%) & Phase mod.\ (mrad) \\
\hline
\multicolumn{4}{l}{\textit{Anterior (Body~12)}} \\
\hline
B33 & $-110.3$ & 0.022 & 98.9 \\
B34 & $-117.6$ & 0.078 & 56.4 \\
B12 & $-115.3$ & 0.082 & 90.0 \\
B11 & $-117.7$ & 0.015 & 92.4 \\
B24 & $-103.2$ & 0.016 & 70.0 \\
B23 & $-78.6$ & 0.006 & 24.3 \\
B31 & $-114.8$ & 0.012 & 42.1 \\
B32 & $-118.0$ & 0.219 & 123.5 \\
B22 & $-115.0$ & 0.068 & 77.0 \\
B21 & $-119.2$ & 0.155 & 141.4 \\
B14 & $-116.5$ & 0.196 & 81.7 \\
B13 & $-115.3$ & 0.031 & 81.9 \\
\hline
\multicolumn{4}{l}{\textit{Posterior (Spine~24)}} \\
\hline
S1P & $-118.5$ & 0.012 & 87.6 \\
S1S & $-119.2$ & 0.014 & 52.1 \\
S1T & $-119.7$ & 0.126 & 539.2 \\
S2T & $-119.8$ & 0.086 & 457.8 \\
S2S & $-119.5$ & 0.009 & 129.4 \\
S2P & $-119.5$ & 0.067 & 198.1 \\
S3P & $-118.9$ & 0.067 & 145.6 \\
S3S & $-118.4$ & 0.008 & 57.4 \\
S3T & $-117.8$ & 0.044 & 109.9 \\
S4T & $-118.6$ & 0.052 & 203.7 \\
S4S & $-110.9$ & 0.003 & 13.6 \\
S4P & $-118.9$ & 0.009 & 70.5 \\
\hline
\end{tabular}}
\end{table}

\begin{table}[htbp]
\centering
\revbrown{\caption{Volunteer~3: Per-channel S-parameter and cardiac modulation depth. Body~18 (anterior, 18\,ch) + Spine~24 (posterior, 9\,ch). Breathhold 22.0\,s, 24 cardiac cycles averaged.}
\label{tab:exp-v3}
\small
\begin{tabular}{lccc}
\hline
Channel & $S_{1,n}$ (dB) & Mag.\ mod.\ (\%) & Phase mod.\ (mrad) \\
\hline
\multicolumn{4}{l}{\textit{Anterior (Body~18)}} \\
\hline
B22 & $-107.0$ & 0.580 & 187.4 \\
B21 & $-109.9$ & 0.093 & 46.6 \\
B35 & $-112.7$ & 0.055 & 40.7 \\
B36 & $-117.5$ & 0.106 & 50.2 \\
B14 & $-111.4$ & 0.017 & 140.1 \\
B13 & $-103.1$ & 0.069 & 26.5 \\
B31 & $-114.5$ & 0.016 & 48.1 \\
B32 & $-112.9$ & 0.038 & 33.8 \\
B24 & $-107.3$ & 0.091 & 133.2 \\
B23 & $-112.8$ & 0.353 & 271.2 \\
B33 & $-92.5$ & 0.024 & 27.1 \\
B34 & $-112.9$ & 0.020 & 46.5 \\
B12 & $-106.6$ & 0.021 & 51.2 \\
B11 & $-116.6$ & 0.057 & 36.6 \\
B26 & $-116.5$ & 0.023 & 90.2 \\
B25 & $-116.0$ & 0.055 & 62.2 \\
B16 & $-115.4$ & 0.094 & 68.9 \\
B15 & $-116.0$ & 0.112 & 84.3 \\
\hline
\multicolumn{4}{l}{\textit{Posterior (Spine~24)}} \\
\hline
S2T & $-118.5$ & 0.125 & 114.2 \\
S2S & $-116.9$ & 0.203 & 92.4 \\
S2P & $-117.0$ & 0.037 & 106.8 \\
S3P & $-117.7$ & 0.103 & 103.6 \\
S3S & $-118.3$ & 0.403 & 140.3 \\
S3T & $-118.1$ & 0.280 & 193.5 \\
S4T & $-119.6$ & 0.465 & 604.3 \\
S4S & $-119.3$ & 0.176 & 141.0 \\
S4P & $-119.2$ & 0.046 & 127.2 \\
\hline
\end{tabular}}
\end{table}
